### 2021-04-14 manuscript.rmd
Log transform, ref #1
added Morey et al. -Abstract - Introduction - Before Bayesian analysis

abstract: |
  The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative content analysis. It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data. Bayesian multilevel regression is suggested to be a, and probably, the only, valid analytical approach. Using the openly available useNews data and the R package brms, we demonstrate how to apply such approach for the analysis of comparative content analysis. We also address common queries of the approach such as choosing the prior distribution and diagnosing the convergence of the model.

@@

This study of ecological effect on individual behaviours has a long tradition in social sciences. A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide. Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries. Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Theoretically with a large enough sample it can be argued that a news article is nested within authors. Such data structure brings two problems: non-atomicity and non-stochasticity.

@@

Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative content analysis.

>>>>

abstract: |
  Comparative content analysis is a frequently used research design in journalism studies. The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative content analysis. It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data. Bayesian multilevel regression is suggested to be a, and probably, the only, valid analytical approach. Using the openly available useNews data and the R package brms, we demonstrate how to apply such approach for the analysis of comparative content analysis. We also address common queries of the approach such as choosing the prior distribution and diagnosing the convergence of the model. Furthermore, we argue that choosing a Bayesian approach also solves the problem of often misinterpreted frequentist confidence intervals.

@@

# cite Durkheim's book about suicide here or a reference discussing Durkheim's reserach
This study of ecological effect on individual behaviours has a long tradition in social sciences. A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide. Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries. Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Theoretically with a large enough sample it can be argued that a news article is nested within authors. Such data structure brings two problems: non-atomicity and non-stochasticity.

# add Hoekstra, R., Morey, R. D., Rouder, J. N., & Wagenmakers, E. J. (2014). Robust misinterpretation of confidence intervals. Psychonomic bulletin & review, 21(5), 1157-1164.
# add Morey, R. D., Hoekstra, R., Rouder, J. N., Lee, M. D., & Wagenmakers, E. J. (2016). The fallacy of placing confidence in confidence intervals. Psychonomic bulletin & review, 23(1), 103-123.
In our paper we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies. While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" (Morey et al., 2016, p. 121) and solve the issue of misinterpreted confidence intervals (Hoeckstra et al., 2014; Rinke & Schneider, 2016). Using the openly available useNews data and the R package brms, we then demonstrate how to apply a Bayesian approach for the analysis of comparative content analysis.

@@

Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative content analysis. Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals Hoeckstra et al., 2014; Rinke & Schneider, 2016). Switching to a Bayesian approach addresses this issue as Bayesian „credible intervals support an interpretation of probability in terms of plausibility" (Morey et al., 2016, p. 120). However, for Bayesian models priors have to be chosen by reserachers.
